\documentclass[12pt]{article}
\usepackage{parskip}
%\usepackage{fullpage}
\usepackage[left=2cm,right=2cm,bottom=2cm,top=2cm]{geometry}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{array}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\usepackage{enumitem}
\usepackage[none]{hyphenat}
\usepackage{graphicx}
\usepackage[large]{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{tipa}
\usepackage{qtree}
\usepackage{enumitem}
\setlist{noitemsep}
\newcommand{\nicebold}{\textbf}
\renewcommand{\labelitemi}{$-$}
\newcommand{\qblank}{\underline{\hspace*{1.5cm}} }
\renewcommand{\arraystretch}{2}


\newcommand{\ba}{
\begin{flushleft}\begin{inparaenum}}

\newcommand{\ea}{\end{inparaenum}\end{flushleft}\end{samepage}\vspace{3mm}\pagebreak[3]}
\newcommand{\q}[1]{
\pagebreak[1]\begin{samepage}
%\begin{minipage}{.8\linewidth} 
\item \textbf{#1} \\
%\end{minipage} %\hfill 
%\underline{\hspace*{1cm}}
\nopagebreak
}
\newcommand{\ans}[1]{\item {#1}\hspace{2mm}}
\newcommand{\fixedans}[1]{\item {#1}\hspace{2mm}}
\newcommand{\balong}{

\begin{minipage}{1\linewidth}
\begin{enumerate}
}
\newcommand{\ealong}{
\end{enumerate}
\end{minipage}
\end{samepage}
\vspace{3mm}
\pagebreak[3]
}
\newenvironment{head}[1]%
{\large \textbf{#1}\begin{itshape}}%
{\end{itshape}\vspace{3mm}\normalsize}%



\begin{document}
\rfoot{Page \arabic{page} of  \pageref{LastPage}}


An exam -- LING 999  (Spring 2016) \hfill Instructor's name\\


\begin{center}
\Large
A Big Exam
\end{center}

\vspace{5mm}
\large
Name \underline{\hspace*{5cm}}
\normalsize
\vspace{5mm}

\begin{head}{Multiple choice.}
Instructions for the Multiple choice section goes here. You can say anything you like.
\end{head}

\begin{multicols}{2}
\begin{enumerate}

\q{Which are the best units of language?}

\balong %use \balong (< "begin answers long") to have each answer on a separate line.
\ans{morphemes}
%Mark the correct answer by putting %correct after it. This allows a key to be generated when the answers are shuffled.
\ans{any unit in Welsh}%correct 
\ans{phonemes}
\ans{syntactic constructions}
\ealong

\q{The \qblank is overused by morphologists as an introductory teaching tool.} %use \qblank to create an underlined blank space of uniform length
\balong
\ans{Iliad}
\ans{Jabberwocky}
\ans{Owl and the Pussycat}
\ans{Jabberwocky; but it's fine.}%correct
\ealong


\q{How many words are there in English}
\ba %use \ba ("begin answers") if you don't want each answer necessarily to be on a separate line
\ans{3}
\ans{6}
\ans{10}
\ans{Lots}%correct
\ea


\q{Which of the following is true of Motherese?}

\balong
\ans{It is known only to Mothers.}
\ans{It is used only by English-speaking parents}
\ans{It does not exist}
\fixedans{None of the above}%correct 
%use \fixedans if you don't want the answer in question to be moved.
\ealong



\q{Al-Sayyid Bedouin Sign Language differs from Nicaraguan Sign Language because}

\balong
\ans{it emerged in Israel, not Nicaragua.}%correct
\ans{it is based on French.}
\ans{it emerged naturally, whereas Nicaraguan Sign Language was invented by Donald Trump.}
\ans{it can be learned by chimps.}
\ealong

\q{Vervet monkeys}

\balong
\ans{are the only primate species to have an ergative-absolutive language.}
\ans{have been subject to many attempts to teach them language.}
\ans{have innate calls whose meanings have to be refined through learning.}%correct
\fixedans{None of the above}
\ealong

\q{Which of the following is not a kind of affix in spoken language?}

\ba
\ans{Circumfix}
\ans{Prefix}
\ans{Infix}
\ans{Quickfix}%correct
\ea

\q{Which of the following languages is not Indo-European?}

\ba
\ans{Klingon}%correct
\ans{Persian}
\ans{Albanian}
\ans{Slovene}
\ea


\q{Categorical perception}

\balong
\ans{makes it easier to understand Kantian ethics.}
\ans{means children are born knowing the phonemes of their parents' language.}
\ans{means that judgements about continuously varying signals do not vary continuously.}%correct
\ans{means that perception is impossible.}
\ealong


\q{The high-amplitude sucking paradigm is}
\balong
\ans{a way of identifying if young babies can distinguish between different stimuli.}%correct
\ans{a way of identifying if young babies are able to suck.}
\ans{useful mainly for visual stimuli.}
\ans{preferred for use with older children and teenagers who can better understand the task.}
\ealong

\q{Find a buttercup and hold it up to your chin. Do you like butter?}
\balong
\fixedans{Yes}
\fixedans{No}
\fixedans{I could have told you that without the buttercup.}
\fixedans{Both a and c} %correct
\ealong




%endofquestions
\end{enumerate}
\end{multicols}

\clearpage


\begin{head}{Short-answer questions.}
Instructions for Short answer questions go here.
\end{head}
\begin{enumerate}

\item (2 points) Explain why you decided to major in Linguistics.

\item (10 points) Choose an unsolved problem in modern Linguistics and solve it. Remember to show your working.

\end{enumerate}
\vspace{6ex}




\clearpage
\begin{center}
Extra space for short answers
\end{center}
%\clearpage
%\begin{center}
%Extra space for short answers
%\end{center}



\end{document}